The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-06-25 WavesData-2019/LatexNotes/notes.tex
NM

% New
\newcommand{\etastd}{\eta_{\text std}}
\newcommand{\ampp}{\mathcal{A}}
\newcommand{\Gibbs}{\mathcal{G}}
\newcommand{\lamfac}{N}
% New
\newcommand{\Hp}{H^{+}}
\newcommand{\Hm}{H^{-}}
\newcommand{\Gp}{\Gibbs^{+}}
\newcommand{\Gm}{\Gibbs^{-}}
\newcommand{\meanp}[1]{\mean{#1}_{+}}
\newcommand{\meanm}[1]{\mean{#1}_{-}}
\newcommand{\skw}{\text{skew}}
\newcommand{\var}{\text{var}}

% New
\newcommand{\depth}{d}
\newcommand{\dup}{\depth^{-}}
\newcommand{\ddn}{\depth^{+}}
\newcommand{\lamup}{\lambda^{-}}
\newcommand{\lamdn}{\lambda^{+}}
\newcommand{\freqp}{f_p}

@@

\subsection{Nondimensionalization of KdV}

We introduce the following characteristic scales
\begin{align}
&a = \etastd = \mean{\eta^2}^{1/2} 
&&\mbox{\em upstream characteristic wave amplitude} \\
&\lamup = \sqrt{g \dup} / \freqp
&&\mbox{\em upstream characteristic wave length}
\end{align}

@@

The statistical matching condition is
\begin{equation}
\meanm{\Hp} = \meanp{\Hp}
\end{equation}
An experimental observation is that the incoming skewness is small, thus
\begin{equation}
\meanm{H_3} \approx 0
\end{equation}
which immediately gives
\begin{equation}
\ampp D^{-3/2} \meanp{H_3} = \mu D^{1/2} \left( \meanp{H_2} - \meanm{H_2} \right)
\end{equation}
or equivalently
\begin{equation}
\label{H3H2}
\meanp{H_3} = \frac{\mu D^{2}}{\ampp} \, \Delta \mean{H_2}
\end{equation}
where $\Delta \mean{H_2} =  \meanp{H_2} - \meanm{H_2}$  indicates the difference between the upstream and downstream values.

>>>>

% New
\newcommand{\depth}{d}
\newcommand{\dup}{\depth^{-}}
\newcommand{\ddn}{\depth^{+}}
\newcommand{\lamup}{\lambda^{-}}
\newcommand{\lamdn}{\lambda^{+}}
\newcommand{\freqp}{f_p}
% New
\newcommand{\meanup}[1]{\mean{#1}_{-}}
\newcommand{\meandn}[1]{\mean{#1}_{+}}
\newcommand{\skw}{\text{skew}}
\newcommand{\var}{\text{var}}

% New
\newcommand{\etastd}{\eta_{\text std}}
\newcommand{\ampp}{\mathcal{A}}
\newcommand{\Gibbs}{\mathcal{G}}
\newcommand{\lamfac}{N}
% New
\newcommand{\Hp}{H^{+}}
\newcommand{\Hm}{H^{-}}
\newcommand{\Gp}{\Gibbs^{+}}
\newcommand{\Gm}{\Gibbs^{-}}

@@

\subsection{Dimensionless variables}

We introduce the following characteristic scales
\begin{align}
&a = \mean{\eta^2}^{1/2} 
&&\mbox{\em upstream characteristic wave amplitude} \\
&\lamup = \sqrt{g \dup} / \freqp
&&\mbox{\em upstream characteristic wave length}
\end{align}
and the dimensionless variables
\begin{align}
&u = \eta/a
&&\mbox{\em dimensionless displacement} \\
&\tilde{x} = \xi/\lamup = (x-ct)/\lamup
&&\mbox{\em dimensionless position} \\
& \tilde{t} = 
\end{align}

@@

The statistical matching condition is
\begin{equation}
\meanup{\Hp} = \meandn{\Hp}
\end{equation}
An experimental observation is that the incoming skewness is small, thus
\begin{equation}
\meanup{H_3} \approx 0
\end{equation}
which immediately gives
\begin{equation}
\ampp D^{-3/2} \meandn{H_3} = \mu D^{1/2} \left( \meandn{H_2} - \meanup{H_2} \right)
\end{equation}
or equivalently
\begin{equation}
\label{H3H2}
\meandn{H_3} = \frac{\mu D^{2}}{\ampp} \, \Delta \mean{H_2}
\end{equation}
where $\Delta \mean{H_2} =  \meandn{H_2} - \meanup{H_2}$  indicates the difference between the upstream and downstream values.
